Hunting experience and prey predictability jointly shape individual foraging specialisation in a predator-prey videogame

### 2022-05-19 manuscript/Chapter3-manuscript.Rmd
update MS introduction

Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@limaPuttingPredatorsBack2002;@schreiberCommunityEffectsPhenotypic2011;@pettorelliChapterTwoIndividual2015;@Michalko.Pekar2016]. Indeed, predator populations are often composed of assemblages of individuals specializing in different foraging strategies or resources [@estesIndividualVariationPrey2003;@tinkerFoodLimitationLeads2008;@kernaleguenDeterminantsIndividualForaging2015:@Phillips.etal2017]. It is now well established that individual foraging specialization cannot be attributed exclusively to intrinsic factors such as sexual, morphological, or age-related differences [@estesIndividualVariationPrey2003;@bolnickEcologyIndividualsIncidence2003; @Woo.etal2008;@bolnickWhyIntraspecificTrait2011]. A growing body of evidence suggests that ecological interactions, such as predator-prey interactions, may instead act as the major drivers of individual foraging specialization [@araujoEcologicalCausesIndividual2011;@toscanoPersonalityForagingBehavior2016]. For instance, predators species often use hunting techniques that are fine-tuned to the type of prey that they encounter [sources : Woo, Estes, tinker, etc] (*and the capacity to learn these strategies may be an important limiting factor to be successful*). Yet, we have very limited knowledge on how intrinsic factors and interactions with prey reciprocally affect predator foraging specialization, and the resulting ecological and fitness consequences of such among individual differences [@Phillips.etal2017].

environmental heterogeneity is a prevailing external factor [@Weimerskirch2007;@ceiaIndividualSpecializationForaging2015;@Phillips.etal2017;@Patrick.etal2021].

This would imply that predators need to develop foraging tactics that are fine tuned to specific prey attributes or prey types [sources: Phillips, Woo, etc.]. *ICI GARDER LES IDÉES MAIS METTRE L'ACCENT SUR LE FAIT QUE C'EST LES PROIES DISPONIBLES AU LIEU DES PROIES MANGÉES*

For instance, predators species often use stereotyped hunting techniques required to capture the type of prey they encounter, such as (dauphins, orcas, etc) [sources : Woo, Estes, tinker, etc]. However, it remains largely unclear *accent sur le fait que on est pas sur les mécanismes qui associe la proie à la tactique*

Hunting experience has been proposed as a potential major driver of the relationship between foraging specialisation and resource use [sources]. Learning how to hunt is crucial for young predators to reach adulthood and survive. (check Urszan et al)
(learning optimises return rates or foraging success)
(apprentissage, search images, prior information)
(par contre, décomposer l'âge de l'expérience est difficile, et particulièrement chez des espèces sur le terrain puisque ça peut impliquer des techniques invasives)
(parler des études qui ont montré que certains spécialistes étaient meilleurs, mais que c'était confondu par l'âge)

@@

>>>>

Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@limaPuttingPredatorsBack2002;@schreiberCommunityEffectsPhenotypic2011;@pettorelliChapterTwoIndividual2015;@Michalko.Pekar2016]. Indeed, predator populations are often composed of assemblages of individuals specializing in different foraging strategies or resources [@estesIndividualVariationPrey2003;@tinkerFoodLimitationLeads2008;@kernaleguenDeterminantsIndividualForaging2015:@Phillips.etal2017]. It is now well established that individual foraging specialization cannot be attributed exclusively to intrinsic factors such as sexual, morphological, or age-related differences [@bolnickEcologyIndividualsIncidence2003;@bolnickWhyIntraspecificTrait2011]. A growing body of evidence suggests that ecological interactions, such as predator-prey interactions, may instead act as the major drivers of individual foraging specialization [@araujoEcologicalCausesIndividual2011;@toscanoPersonalityForagingBehavior2016]. For instance, predators species often use hunting techniques that are fine-tuned to the type of prey that they encounter [@Davoren.etal2003;@estesIndividualVariationPrey2003;@Woo.etal2008;@courbinShorttermPreyField2018], and their capacity to learn through experience how to effectively use them is essential to maintain foraging success. Yet, we have very limited knowledge on how predator foraging specialization develops through experience and interactions with prey, and the resulting ecological consequences of such among individual behavioural differences for predator-prey interactions [@Phillips.etal2017].

Hunting experience has been proposed as a potential major driver of the relationship between foraging specialisation and resource use [sources]. Learning how to hunt is crucial for young predators to reach adulthood and survive. (check Urszan et al)
(learning optimises return rates or foraging success)
(apprentissage, search images, prior information)
(par contre, décomposer l'âge de l'expérience est difficile, et particulièrement chez des espèces sur le terrain puisque ça peut impliquer des techniques invasives)
(parler des études qui ont montré que certains spécialistes étaient meilleurs, mais que c'était confondu par l'âge)
[*références learning : phillips, Haage(minks), Tinker (théorique), Weimerskirch ()*]

@@

sources générales sur heterogeneité[@Weimerskirch2007;@ceiaIndividualSpecializationForaging2015;@Phillips.etal2017;@Patrick.etal2021].
